Holomorphic field theories and higher algebra

### 2023-01-28 draft.tex
added a small remark in section 4

A key idea for us is that much of the content in field theories --- both classical and quantum --- is captured by factorization algebras.
We will introduce that concept now, in the style that sheaves are defined, so first we describe {\em pre}\/factorization algebras and then impose a local-to-global condition to characterize factorization algebras.
Their local structure encompasses the behavior we saw in the preceding section, where $E_d$ algebras captured topological field theories on $\RR^d$ and $\PDisc_d$ algebras captured holomorphic field theories on~$\CC^d$.
Factorization algebras allow one to work on smooth manifolds, and complex manifolds, more generally;
their global behavior encompasses constructions like Hochschild homology and conformal blocks.
We will then sketch the main theorem of \cite{CG2}, 
which explains a precise and general relationship between quantum field theories and factorization algebras.
Finally, we describe some special features and interesting applications of factorization algebras of holomorphic field theories.

\begin{rmk}
Beilinson and Drinfeld introduced the notion of factorization algebras in their work on chiral conformal field theory \cite{BD},
and their version has had great success in algebraic geometry and representation theory,
particularly in the setting of the geometric Langlands program.
Gaitsgory, Francis, and Lurie ported the spirit of this notion into the setting of  manifolds,
developing topological chiral homology \cite{LurieHA} and factorization homology \cite{AF}
for questions in algebraic topology.
Motivated by these efforts (and benefiting from conversations as those works were in progress), 
Kevin Costello and the first author developed a version that works well for a broad class of quantum field theories and for more differential-geometric settings~\cite{CG1,CG2}.
\end{rmk}

>>>>

A key idea for us is that much of the content in field theories --- both classical and quantum --- is captured by factorization algebras.
We will introduce that concept now, in the style that sheaves are defined, so first we describe {\em pre}\/factorization algebras and then impose a local-to-global condition to characterize factorization algebras.
Their local structure encompasses the behavior we saw in the preceding section, where $E_d$ algebras captured topological field theories on $\RR^d$ and $\PDisc_d$ algebras captured holomorphic field theories on~$\CC^d$.
Factorization algebras allow one to work on smooth or complex manifolds and hence bring in global aspects of geometry.
Their global behavior encompasses constructions like Hochschild homology (for $E_1$ algebras extended as factorization algebras on $S^1$) and conformal blocks (for $\PDisc_1$ algebras extended as factorization algebras to Riemann surfaces).
We will then sketch the main theorem of \cite{CG2}, 
which explains a precise and general relationship between quantum field theories and factorization algebras.
Finally, we describe some special features and interesting applications of factorization algebras of holomorphic field theories.

\begin{rmk}
Beilinson and Drinfeld introduced the notion of factorization algebras in their work on chiral conformal field theory \cite{BD},
and their version has had great success in algebraic geometry and representation theory,
particularly in the setting of the geometric Langlands program.
Francis, Gaitsgory, and Lurie ported the spirit of this notion into the setting of manifolds,
developing topological chiral homology \cite{LurieHA} and factorization homology \cite{AF}
for questions in algebraic topology.
Motivated by these efforts (and benefiting from conversations as those works were in progress), 
Kevin Costello and the first author developed a version that works well for a broad class of quantum field theories and for more differential-geometric settings~\cite{CG1,CG2}.
These approaches share a common spirit but have important technical differences.
A detailed comparison between the versions for locally constant factorization algebras exists \owen{good refs?},
but a detailed comparison between the Beilinson-Drinfeld and Costello-Gwilliam version is currently open.
(See, however, section \owen{fill out } of \cite{HenKap} for important steps in that direction.)
\end{rmk}
